### 2021-09-02 documentos/pce.tex
push porque tengo que hacer
Things went wrong...

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_0,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

\begin{figure} % {{{
	\centering
	\hfill \hfill
	\includegraphics[height=2.5cm]	{tablero_1qubit}
	\hfill
	\includegraphics[height=2.5cm]{tablero_2qubits}
	\hspace{1mm}
	\includegraphics[height=2.7cm]{rho-3q}
	\hfill \hfill
	\caption{From left to right representations of identity map
	(also PCE operations) of 1, 2 and 3 qubits, respectively.}
	\label{fig:PCE_figs}
\end{figure} % }}}

>>>>

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{

\begin{itemize}
\item Quizá en este punto hablar un poco de decoherencia de $N$ qubits, como 
solo para motivar los PCEs y decir que se va a ligar al final.

\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

\begin{figure} % {{{
	\centering
	\hfill \hfill
	\includegraphics[height=2.5cm]	{tablero_1qubit}
	\hfill
	\includegraphics[height=2.5cm]{tablero_2qubits}
%	\hspace{1mm}
%	\includegraphics[height=2.7cm]{rho-3q}
	\hfill \hfill \hfill
	\caption{From left to right representations of identity map
	(also PCE operations) of 1 and 2 qubits, respectively.}
	\label{fig:PCE_figs}
\end{figure} % }}}
